### 2025-04-16 multiple-regression.qmd
20250416 - fix and newdata prediction

ggplot2::ggplot(
  data = player_stats_seasonal %>%
    filter(position_group %in% c("WR")),
  mapping = aes(
    x = height)
) +
  geom_histogram(
    aes(y = after_stat(density)),
    color = "#000000",
    fill = "#0099F8"
  ) +
  geom_density(
    color = "#000000",
    fill = "#F85700",
    alpha = 0.6 # add transparency
  ) +
  geom_rug() +
  labs(
    x = "Fantasy Points",
    y = "Height (inches)",
    title = "Density Plot of Player Height with Histogram and Rug Plot"
  ) +
  theme_classic() +
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title

@@

We could also generate the model-implied prediction of fantasy points for any value of the [predictor variables](#sec-correlationalStudy).
For instance, here are the number of fantasy points expected for a Wide Receiver who is 23 years old, who is 6'2" tall (72 inches), and weighs

>>>>

ggplot2::ggplot(
  data = player_stats_seasonal %>%
    filter(position_group %in% c("WR")),
  mapping = aes(
    x = height)
) +
  geom_histogram(
    aes(y = after_stat(density)),
    color = "#000000",
    fill = "#0099F8"
  ) +
  geom_density(
    color = "#000000",
    fill = "#F85700",
    alpha = 0.6 # add transparency
  ) +
  geom_rug() +
  labs(
    x = "Height (inches)",
    y = "Density",
    title = "Density Plot of Player Height with Histogram and Rug Plot"
  ) +
  theme_classic() +
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title

@@

We could also generate the model-implied prediction of fantasy points for any value of the [predictor variables](#sec-correlationalStudy).
For instance, here are the number of fantasy points expected for a Wide Receiver who is 23 years old, is 6'2" tall (72 inches), weighs 200 pounds, and has a 3% target share:

```{r}
predict(
  quadraticTermsRegressionModel,
  newdata = data.frame(
    age = 23,
    height = 72,
    weight = 200,
    target_share = 3
  )
)
```

predictedValue <- predict(
  quadraticTermsRegressionModel,
  newdata = data.frame(
    age = 23,
    height = 72,
    weight = 200,
    target_share = 3
  )
)
```

The player would be expected to score `r petersenlab::apa(predictedValue, decimals = 0)` fantasy points.
